Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-26 paper.tex
updating the experiments section
Adding description of special editorial cases

%***TODO***: talking about the machines used
% Please don't use real text for TODOs- JJ
%Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
%(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.

@@

This section will present some experiments conducted on the data concerning four different example cases, namely:
\begin{itemize}
    \item best seller editorial
    \item medium seller editorial
    \item best varied editorial
    \item medium varied editorial
\end{itemize}

%***TO DO ***: Justify the special cases (why we have chosen them).

Table XX shows the details of each of these editorials.

\begin{table}
\caption{Description of editorials considered as special cases.
\label{tab:desc_editorials}}
\centering{}%
\begin{tabular}{|r|l|l|l|}
\hline 
 & Different books sold & Total copies sold & Description\\
\hline 
\textit{All editorials} & 6083 & 3201645 & 209 editorials\\
\hline 
\textit{UDL704} & 293 & 58236 & Editorial with most different\\ 
       &     &       & books sold\\
\hline 
\textit{UDLU11} & 180 & 249481 & Editorial with medium number\\ 
       &     &       &  of different books sold\\
\hline 
\textit{UDL929} & 216 & 460752 & Best selling editorial\\
\hline 
\textit{UDLW12} & 97 & 2635 & Medium selling editorial\\
\hline 
\end{tabular}
\end{table}

>>>>

%***TODO***: talking about the machines used
% Done - %---  Sam
% Please don't use real text for TODOs- JJ
%Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
%(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.

All experiments have been conducted on an  Intel(R) Core(TM) i5-2400 CPU at 3.10Ghz with a memory of 4 GB running Windows 7 professional 32bit operating system and Java JRE\_1.7.0\_72.

@@

This section presents further experiments conducted on data concerning four interesting special editorial cases. These editorials were selected as representative cases which could be very interesting for decision makers and managers in the domain. The four cases are described as follows:

\begin{itemize}
    \item Best seller editorial: this case represents the editorial that sells the highest number of copies regardless the title of the books sold. Therefore, it is an example of a case on a higher business scale.
    \item Medium seller editorial: this represents an editorial that sells medium number of copies compared to the other editorials (Medium business scale). 
    \item Highest variation editorial: this is an example of an editorial that follows a strategy in publishing a very wide range of different titles.
    \item Medium varied editorial: this case represents an editorial that has a median rank between the other editorial regarding the variety of titles sold.
\end{itemize}

Table \ref{Table:special_cases} shows the details of each of the selected editorials.

\begin{table}
\caption{Description of editorials considered as special cases.
\label{tab:desc_editorials}}
\centering{}%
\begin{tabular}{|r|l|l|l|}
\hline 
 & Different books sold & Total copies sold & Description\\
\hline 
\textit{All editorials} & 6083 & 3201645 & 209 editorials\\
\hline 
\textit{UDL704} & 293 & 58236 & Editorial with most different\\ 
       &     &       & books sold\\
\hline 
\textit{UDLU11} & 180 & 249481 & Editorial with medium number\\ 
       &     &       &  of different books sold\\
\hline 
\textit{UDL929} & 216 & 460752 & Best selling editorial\\
\hline 
\textit{UDLW12} & 97 & 2635 & Medium selling editorial\\
\hline 
\end{tabular}
\label{Table:special_cases}
\end{table}
